---
title: "CURRICULUM VITAE"
subtitle: "« Pleasure in the job puts perfection in the work. »"
output:
  distill::distill_article:
    toc: true
---

## Download my Curriculum Vitae

```{r cv, echo = FALSE}

#Functions from jhelvy (https://github.com/jhelvy)
make_icon <- function(icon) {return(htmltools::tag("i", list(class = icon)))}
make_icon_text <- function(icon, text) {return(htmltools::HTML(paste0(make_icon(icon), " ", text)))}
icon_link <- function(icon = NULL, text = NULL, url = NULL) {
  if (!is.null(icon)) {text <- make_icon_text(icon, text)}
  return(htmltools::a(href = url, text, class = "icon-link"))
  }

#Création d'un icone contenant le lien vers le cv 
icon_link(text = "Curriculum Vitae", url  = "links/cv.pdf") 
```

<br>

## Research Interests

Anthropogenic stressors & fish

<br>

## Publications

```{r setup, include=FALSE, echo=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(readxl)
```

```{r, echo=FALSE, results='asis'}

# Charger les données à partir du fichier Excel
pub_data <- readxl::read_excel("pub_list/pub_list.xlsx")
pub_data <- subset(pub_data, Category %in% c("Article", "Poster", "Presentation"))

# Extraire les catégories uniques
categories <- unique(pub_data$Category)

# Parcourir les catégories et afficher les publications correspondantes
for (cat in categories) {
  
  # Afficher le titre de la catégorie
  cat(paste0("<h3>", cat, "</h3>\n"))
  
  # Filtrer les données pour cette catégorie
  cat_data <- subset(pub_data, Category == cat)
  
  for (i in 1:nrow(cat_data)) {
    
  # Variables
  title <- cat_data$Title[i]
  year <- cat_data$Year[i]
  journal <- cat_data$Journal[i]
  journal_ref <- cat_data$JournalRef[i]
  filename <- cat_data$FileName[i]
  doi <- cat_data$DOI[i]
  link <- cat_data$Link[i]
  image_name <- gsub(".pdf", ".png", filename)
  
  }

  # Parcourir les lignes et afficher les informations formatées
  for (i in 1:nrow(cat_data)) {
    
    # Article
    if (cat == "Article") {
      cat(
        "<p style='text-align: justify;'><strong>", title, "</strong>", 
        paste0("(", year, "). "), 
        "<em>", paste0(journal, ", "), "</em>", 
        paste0(journal_ref, ". "), 
        paste0(doi, ". "),
        "<a href='", filename, "' style='color:red;'>Link to PDF</a></p>\n\n"
      )
      
    # Poster
    } else if (cat == "Poster") {
      cat(
        "<p style='text-align: justify;'><strong>", title, "</strong>", 
        paste0("(", year, "). "), 
        "<em>", paste0(journal, ", "), "</em>", 
        paste0(doi, ". "),
        "<a href='", filename, "' style='color:red;'>Link to PDF</a></p>\n\n"
      )
    
    # Presentation
    } else if (cat == "Presentation") {
      cat(
        "<p style='text-align: justify;'><strong>", title, "</strong>", 
        paste0("(", year, "). "), 
        "<em>", paste0(journal, ", "), "</em>", 
        paste0(doi, ". "),
        "<a href='", filename, "' style='color:red;'>Link to PDF</a></p>\n\n"
      )
    
    }
  }
}
```

<br>

## Skills

Ecology : fish, estuary, rivers, catchments, spawning grounds

Anthopogenic : heatwaves, chemicals

Ecotoxicology : PAF method

Modelling : time series, linear model

Coding : R (RStudio), SQL (DBeaver), Git (Github)

Microsoft : Word, Excel, Powerpoint

<br>

## My career summary

```{r, echo = FALSE}

# Packages
library(leaflet)
library(tidyverse)

# Data with coordinates
data <- read_excel("links/career.xlsx") %>% 
  rename(Longitude = X, Latitude = Y) 

# Create the leaflet map
map <- leaflet(data) %>%
  addTiles() %>%
  addMarkers(~Latitude, ~Longitude, 
             popup = ~paste("<strong>Country:</strong>", Country, "<br>",
                            "<strong>Region:</strong>", Region, "<br>",
                            "<strong>City:</strong>", City, "<br>",
                            "<strong>Years:</strong>", Year_start, "-", Year_end, "<br>",
                            "<strong>Type:</strong>", Type))

# Display the map
map
```

<br>

## Research jobs

**LIENSs, AMARE/BIATSS, Projet ECHO**

*La Rochelle (France) - October 2024 to now*

-   ...

-   ...

**Qualyse, Pôle Croissance et Innovation, Projet PLASTyre**

*La Rochelle (France) - September 2024 to October 2024*

-   ...

-   ...

**INRAE, EABX, FREEMA ([website](https://eabx.bordeaux-aquitaine.hub.inrae.fr/))**

*Cestas-Gazinet (France) - December 2023 to July 2024*

-   Studying the effects of estuarine heatwaves in fish communities

-   Writing an article : work in progress...

**INRAE, EABX, FREEMA ([website](https://eabx.bordeaux-aquitaine.hub.inrae.fr/))**

*Cestas-Gazinet (France) - September 2023* *to November 2023*

-   Writing an article : "Assessing the impact of chemical pollution on endangered migratory fish within a catchment using a Potentially Affected Fraction of species (PAF) approach: a case study at main rivers and spawning ground scales"

<br>

## Educational background

**Master of "Environmental Sciences" (SPE) in "Environmental Management and Coastal Ecology" (GEEL) -\> [website](https://formations.univ-larochelle.fr/msc-environmental-management-and-coastal-ecology)**

*La Rochelle University (2021-2023)*

-   Data Analysis, Geographical Information System, Biogeochemical Cycles, Ichtyology, Coastal Sampling, Oceanography, Impacts of Human Activities, *etc.*

-   Protocol for sampling, sorting, selection of biological samples and data analysis in the Baie de l'Aiguillon mudflat

**Master of "Integrated Management of Tropical Coastal Areas" (GIACT) -\> [website](https://www.sep.ucr.ac.cr/ppgiact-inicio)**

*University of Costa Rica (2022-2023)*

-   Courses taught entirely in Spanish

-   Ecological Economics, Oceanography, Politics, Governance, Integrated Tropical Coastal Management, Fisheries Management, *etc.*

-   Protocol for sampling water characteristics in estuaries with different anthropogenic impacts

**License of Organismal and Population Biology (BOP) -\> [website](https://formations.univ-angers.fr/fr/offre-de-formation/licence-lmd-LILMD/sciences-technologies-sante-STS/licence-sciences-de-la-vie-et-de-la-terre-KQJGEOCC/l3-parcours-biologie-des-organismes-et-populations-LMETB9C9/parcours-bop-LMEXXMTB.html)**

*Angers University (2018-2021)*

-   Genetics, Ecotoxicology, Zoology, Ethology, Physiology, Microbiology, Anatomy, Population Dynamics, *etc.*

**Scientific Baccalaureate in Life and Earth Sciences -- 2018 (sports-study programme) -\> [website](https://saintthomasdaquin.org/section-sportive/cyclisme-masculin/)**

*Saint Thomas D'Aquin high school*

-   High-level athlete: organization, autonomy and rigor

<br>

## Volunteer

**4P SCIENSEAS (2022) -\> [website](https://4pscienseas.org/)**

*Photo Project -- Route du Plastique*

-   Bibliographical work to raise public awareness of the problem of plastic pollution
-   Recreational activities to raise public awareness of the problem of plastic pollution

<br>

## Sports Awards

**Cyclism (National level)**

*VC Lucéen (2020-2022) - National level*

*Angers Cyclisme (2018-2019) - National level*

*UC Nantes Atlantique (2017) - National level*

**Basket-ball (Regional level)**
